Proposed Solution

### 2017-01-24 CAV17/secs/trans.tex
stuff

A probabilistic type is a set of counts over a set $\mathcal{T}$ of basic types.
Formally, we define a space of probabilistic types $\tilde{\mathcal{T}}$, where $\ptype \in \tilde{\mathcal{T}}$ has a form $\ptype=\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$. 
Every keyword $k\in\keys$ has a probabilistic type, expressed $k:\ptype$, which, without any evidence, remains {\scriptsize EMPTY}.
The count for $(\tau_i,c_i) \in \ptype$ is incremented each time a new example value that matches to type $\tau_i$ is encountered for a particular key, using the update notation $\update$.
We also denote the set of key-value pairs with $C$ and a keyword value pair that exists in some configuration file as $(k,v) \in C$.

{
\setlength{\abovecaptionskip}{-.05pt}
\setlength{\belowcaptionskip}{-15pt}
\begin{figure}
\begin{mathpar}
\hspace{-1cm} %no idea why, but this is better than \centering here
\inferrule* [Right=Empty]
{\\}
{k:[\ast = 0]}
\and
\inferrule* [Right=bool\_int]
{(k,v) \in C \\ v \in \{0,1\} \\ k:\ptype}
{k:\ptype\update[int\pluseq 1,bool\pluseq 1]}
\and
\inferrule* [Right=bool]
{(k,v) \in C \\ v \in \{ON,OFF\} \\ k:\ptype}
{k:\ptype\update[bool\pluseq 1]}
\\
\and
\inferrule* [Right=bool\_resolve]
{k:\ptype \\ \ptype \models bool \geq 2 \land \ast \leq 1}
{k :: bool}
\\
\and
\inferrule* [Right=eq\_rule]
{k1 :: \tau \\ k2 :: \tau \\ \tau \in \mathcal{T}}
{eq(k1,k2) :: Rule}
\end{mathpar}
\caption{Type judgments for Boolean equality rules with probabilistic types}
\label{fig:ptypes}
\end{figure}
}

In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
In this case, we allow a probabilistic type to resolve to a Boolean if we have two counts for Boolean, and no more than one count for any other basic type ($\ast$).
We use the notation, $\ptype \models p$, to denote a probabilistic type whose counts hold on the predicate $p$.
Taking the type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
Using the rules from Fig.~\ref{fig:ptypes}, we would derive the probabilistic type \texttt{bar}$:[bool=3,int=1]$, which then resolves to \texttt{bar}$::bool$.

>>>>

A probabilistic type is a set of counts over a set $\mathcal{T}$ of basic types.
Formally, we define a space of probabilistic types $\tilde{\mathcal{T}}$, where $\ptype \in \tilde{\mathcal{T}}$ has a form $\ptype=\{(\tau_1, c_1),\ldots,(\tau_n, c_n)\}$, such that $\tau_i \in \mathcal{T}$, $c_i \in \mathbb{Z}$. 
Every keyword $k\in\keys$ has a probabilistic type, expressed $k:\ptype$.
The count for $(\tau_i,c_i) \in \ptype$ is incremented each time a new example value that matches to type $\tau_i$ is encountered for a particular key, using the update notation $\update$.
We also denote the set of key-value pairs with $C$ and a keyword value pair that exists in some configuration file as $(k,v) \in C$.

Fig.~\ref{fig:ptypes} provides a fragment of a calculus for type judgments for deriving Boolean equality rules with probabilistic types.
We use the notation, $\ptype \models p$, to denote a probabilistic type whose counts hold on the predicate $p$. For a $\ptype$ with $|\tau_i|$ 
we denote $c_i$, and $*$ is shorthand for all basic types. When there is no evidence for a type $\tau$ we call this empty type ({\scriptsize EMPTY}). Initially, before we count any type, all types are set to empty. 
In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.

{
\setlength{\abovecaptionskip}{-.05pt}
\setlength{\belowcaptionskip}{-15pt}
\begin{figure}
\begin{mathpar}
\hspace{-1cm} %no idea why, but this is better than \centering here
\inferrule* [Right=Empty]
{\\}
{k:[\ast = 0]}
\and
\inferrule* [Right=bool\_int]
{(k,v) \in C \\ v \in \{0,1\} \\ k:\ptype}
{k:\ptype\update[int\pluseq 1,bool\pluseq 1]}
\and
\inferrule* [Right=bool]
{(k,v) \in C \\ v \in \{ON,OFF\} \\ k:\ptype}
{k:\ptype\update[bool\pluseq 1]}
\\
\and
\inferrule* [Right=bool\_resolve]
{k:\ptype \\ \ptype \models |bool| \geq M \land |\ast| \leq N}
{k :: bool}
\\
\and
\inferrule* [Right=eq\_rule]
{k_1 :: \tau \\ k_2 :: \tau \\ \tau \in \mathcal{T}}
{eq(k_1,k_2) :: Rule}
\end{mathpar}
\caption{Type judgments for Boolean equality rules with probabilistic types}
\label{fig:ptypes}
\end{figure}
}

Taking these type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}. The result is the probabilistic type \texttt{bar}$:[bool=3,int=1]$. By setting $M=3, N=1$, we resolve it to \texttt{bar}$::bool$.
